### 2015-02-21 paper_40_mpi.tex
more schedule work

                    Application ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Scheduled Start Date & Date & Required \\
                    \myrowcolour%
                    Scheduled Finish Date & Date & Required \\
                    Actual Start Date & Date  & Optional \\
                    \myrowcolour%
                    Actual Finish Date & Date  & Required \\

@@

>>>>

                    Project ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Scheduled Start Date & Date & Required \\
                    \myrowcolour%
                    Scheduled Finish Date & Date & Required \\
                    Actual Start Date & Date  & Optional \\
                    \myrowcolour%
                    Actual Finish Date & Date  & Required \\

@@

                \begin{displaymath}
                    \Delta_i = \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1}
                \end{displaymath}
                where
                \begin{itemize}
                    \item $F_{a_i}$ the actual finish date of project $i$
                    \item $F_{s_i}$ the scheduled finish date of project $i$
                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                    \item $\Delta_i$ the percent the schedule was missed for project $i$
                \end{itemize}

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data.
